Manuscript

### 2017-11-02 manuscript.Rmd
Added new lines of code that allowed me to check the impacts for Boston and NYC.

# variables
cities <- c("denver", "boston", "nyc")
```

@@

@@

tract_shapes <- list(denver_tracts, boston_tracts, nyc_tracts)
park_shapes <- list(denver_parks, boston_parks, nyc_parks)
```

@@

#denver_tracts2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
plot(denver_tracts)

#denver_parks2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
plot(denver_parks)
```

@@

```{r}
denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = denver_plots)
```

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -5))
#regression_data[[2]]["park_ls"] <- calculate_park_logsums(
 # boston_tracts, boston_parks, betas = c(.00001, -30))
#regression_data[[3]]["park_ls"] <- calculate_park_logsums(
 # nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

@@

  names(models) <- cities[1:3]
  return(models)
})

>>>>

# variables
cities <- c("denver", "boston", "nyc")
#cities <- c("boston", "denver", "nyc")
#cities <- c("nyc", "boston", "denver")
```

@@

## I removed the really large Northeasternmost census tracts from Boston as well as a number of private parks. I also removed professional sports stadiums from the NYC parks dataset.

@@

#tract_shapes <- list (boston_tracts, denver_tracts, nyc_tracts)
tract_shapes <- list(denver_tracts, boston_tracts, nyc_tracts)
#tract_shapes <- list(nyc_tracts, boston_tracts, denver_tracts)
#park_shapes <- list(boston_parks, denver_parks, nyc_parks)
park_shapes <- list(denver_parks, boston_parks, nyc_parks)
#park_shapes <- list(nyc_parks, boston_parks, denver_parks)
```

@@

#denver_tracts2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
#plot(boston_tracts)
plot(denver_tracts)
#plot(nyc_tracts)

#denver_parks2 <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
#plot(boston_parks)
plot(denver_parks)
#plot(nyc_parks)
```

@@

```{r}
#boston_plots <- spTransform(boston_tracts, CRSobj = CRS("+init=epsg:4326"))
denver_plots <- spTransform(denver_tracts, CRSobj = CRS("+init=epsg:4326"))
#nyc_plots <- spTransform(nyc_tracts, CRSobj = CRS("+init=epsg:4326"))
library(leaflet)
leaflet() %>%
  addTiles() %>%
  #addPolygons(data = nyc_plots)
  addPolygons(data = denver_plots)
  #addPolygons(data = boston_plots)
```

@@

Calculate the logsum given the tracts and parks dataset:
```{r accessibility}
regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  denver_tracts, denver_parks, betas = c(.00001, -15))
#regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  #boston_tracts, boston_parks, betas = c(.00001, -5))
#regression_data[[1]]["park_ls"] <- calculate_park_logsums(
  #nyc_tracts, nyc_parks, betas = c(.00001, -15))
#regression_data[[2]]["park_ls"] <- calculate_park_logsums(
 # boston_tracts, boston_parks, betas = c(.00001, -30))
#regression_data[[3]]["park_ls"] <- calculate_park_logsums(
 # nyc_tracts, nyc_parks, betas = c(.00001, -5))
```

@@

  names(models) <- cities[1:1]
  return(models)
})
